Declarative Methods Term Project: \\ JumanG

### 2013-05-03 doc/paper.tex

\subsubsection{Radial Solver}
Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
Rarely, however, has it been used to display graphs. We implemented a solver that lays out a graph radially, from the center out.
These

>>>>

\subsubsection{Radial Solver}
Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
It is unusual, however, to use it to display graphs. We wrote our solver to evenly distribute nodes around the root at each level,
rather than using the traditional style of weighting them based on the number of subnodes as is typical for a solver like this. 
On graphs that are smaller than
